Modeling vertical-axis cross-flow turbine wakes

### 2015-08-11 paper.tex
Note that TKE is zero for SA and that variances are from downsampled time series; fixes #17 and fixes #20

Turbulence kinetic energy profiles are shown in Figure~\ref{fig:k-profiles}.
Note that there are two profiles for each---one computed from the components
from the Reynolds stress tensor $R$:

\begin{equation}
k = \frac{1}{2} \left( R_{xx} + R_{yy} + R_{zz} \right);
\label{eq:k}
\end{equation}
and one that includes unsteadiness in the Reynolds-averaged velocity
\begin{equation}
k_{\mathrm{tot}} = k + \frac{1}{2} \left( 
\overline{U^\prime}^2 + 
\overline{V^\prime}^2 + 
\overline{W^\prime}^2 \right),
\label{eq:ktot}
\end{equation}
where $U^\prime = U - \overline{U}$.

>>>>

Turbulence kinetic energy profiles are shown in Figure~\ref{fig:k-profiles}. The
turbulence kinetic energy is calculated as
\begin{equation}
k = k_{\mathrm{RA}} + \frac{1}{2} \left( 
\overline{U^\prime}^2 + 
\overline{V^\prime}^2 + 
\overline{W^\prime}^2 \right),
\label{eq:k}
\end{equation}
where $U^\prime = U - \overline{U}$ and $k_{\mathrm{RA}}$ is the kinetic energy
calculated by the turbulence model, which is zero for the SA model. Note that
the statistics of the Reynolds-averaged velocity are calculated from a time
series that has been downsampled to 50 Hz. It is assumed that this is far enough
from the blade passage frequency that differences from the variance in the
original velocity will be negligible
